LAGOS lake depth

### 2021-08-04 figures/01_geometry.Rmd
linting

gg_pntrng_deepest <- st_drop_geometry(dt) %>%
    dplyr::filter(!is.na(reservoir_class)) %>%
  group_by(reservoir_class) %>%
  summarize(dist_deepest = list(tibble::enframe(
    quantile(dist_deepest, probs = c(0.05,0.5,0.95), na.rm = TRUE)))) %>% 
  unnest() %>%
  tidyr::spread(name, value) %>%
  ggplot() +
geom_pointrange(aes(x = reservoir_class, y = `50%`, 
                      ymin = `5%`, ymax = `95%`)) +
  ylab("Deepest point distance (m)") + xlab("")

gg_pntrng_viscenter <- st_drop_geometry(dt) %>%
    dplyr::filter(!is.na(reservoir_class)) %>%
  group_by(reservoir_class) %>%
  summarize(dist_viscenter = list(tibble::enframe(
    quantile(dist_viscenter, probs = c(0.05,0.5,0.95), na.rm = TRUE)))) %>% 
  unnest() %>%
  tidyr::spread(name, value) %>%
  ggplot() +
geom_pointrange(aes(x = reservoir_class, y = `50%`, 
                      ymin = `5%`, ymax = `95%`)) +
  ylab("Distance to lake center (m)") + xlab("")

@@

get_pnt_map <- function(x){
  # x <- 3
  # x <- which(dt$llid == 257862)
  lg_example <- LAGOSUSgis::query_gis(
    "LAGOS_US_All_Lakes_1ha", "lagoslakeid", dt$llid[x])
  crs_example <- st_crs(
    raster(list.files(paste0("../data/", tolower(dt$state[x]), "_bathy"), 
               include.dirs = TRUE, full.names = TRUE)[1])
    )
  st_crs(dt$pnt_deepest)   <- crs_example
  st_crs(dt$pnt_viscenter) <- crs_example

@@

# get_pnt_map(which(dt$llid == 5636))
# get_pnt_map(which(dt$llid == 257862))
# cowplot::plot_grid(get_pnt_map(which(dt$llid == 3791)) +
#                      ggtitle(3791), 
#                    get_pnt_map(which(dt$llid == 2772)) +
#                      ggtitle(2772), 
#                    get_pnt_map(which(dt$llid == 2655)) +
#                      ggtitle(2655), 
#                    get_pnt_map(which(dt$llid == 1822)) +
#                      ggtitle(1822)
#                    )

```

@@

gg_scatter_slope <- function(x, y, dt){
  ggplot(data = dt) + 
    geom_point(aes(UQ(rlang::sym(x)), UQ(rlang::sym(y))))
}

@@

rsq <- round(broom::glance(lm(dist_viscenter ~ dist_deepest, data = dt))$r.squared, 2)
gg_dist_base <- st_drop_geometry(dt) %>%
  dplyr::filter(!is.na(shape_class)) %>%
  dplyr::filter(dist_viscenter >= dist_deepest) %>%
  dplyr::filter(dist_deepest < 3200) %>%
  ggplot(aes(x = dist_deepest, y = dist_viscenter)) + 
  geom_point(size = 1) +
  geom_smooth(method = "lm", se = FALSE) +
  annotate("text", x = 2550, y = 400, label = paste0("R^2 == ", rsq),
                                parse = TRUE, size = text_size-0.7) +
  annotate("label", x = 1800, y = 150, 
           label = get_formula(
             lm(dist_viscenter ~ dist_deepest, data = st_drop_geometry(dt))), 
           size = text_size-0.85, fill = "white", label.size = NA) +
  labs(color = "") +
  xlab("Deepest point distance (m)") +
  ylab("Distance to \n lake center (m)") +
  xlim(0, 3000) +
  theme_opts

@@

rsq <- round(broom::glance(lm(nearshore_slope_mean ~ inlake_slope_pnt, data = test))$r.squared, 2)
gg_slope_base <- ggplot(data = test) + 
  geom_point(aes(nearshore_slope_mean, inlake_slope_pnt), size = 1) +
  geom_smooth(aes(nearshore_slope_mean, inlake_slope_pnt), method = "lm", se = FALSE) +
  geom_rect(xmin = 0.28, xmax = 0.42, ymin = 0, ymax = 0.05,
  alpha = 1, fill = "white") +
  annotate("text", x = 0.34, y = 0.05, label = paste0("R^2 == ", rsq),
                                parse = TRUE, size = text_size-0.7) +
  annotate("label", x = 0.27, y = 0.01, 
           label = get_formula(
             lm(inlake_slope_pnt ~ nearshore_slope_mean, data = test)), 
           size = text_size-0.85, fill = "white", label.size = NA) +
  # geom_abline(slope = 1, intercept = 0) +
  xlab("Nearshore slope (mean)") +
  ylab("In-lake slope") +
  labs(color = "") +
  theme_opts

cowplot::plot_grid(
  gg_dist_base, 
  gg_slope_base, 
  rel_widths = c(1, 0.9)
)

```

@@

gg_dists_base <- dt %>%
  # dplyr::filter(!is.na(shape_class)) %>%
  dplyr::filter(dist_viscenter >= dist_deepest) %>%
  dplyr::filter(dist_deepest < 3200) %>%
  ggplot(aes(x = dists_deepest, y = dist_viscenter)) + 
  geom_point(size = 1) +
  geom_smooth(method = "lm", se = FALSE) +
  annotate("text", x = 1800, y = 400, label = paste0("R^2 == ", rsq),
                                parse = TRUE, size = text_size-0.7) +
  annotate("label", x = 1200, y = 150, 
           label = get_formula(
             lm(dist_viscenter ~ dists_deepest, data = dt)), 
           size = text_size-0.85, fill = "white", label.size = NA) +
  labs(color = "") +
  xlab("Deepest point distance (m)") +
  ylab("Distance to \n lake center (m)") +
  xlim(0, 2000) +
  theme_opts

@@

gg_slope_alternative <- function(nearshore_var, inlake_var, dt){
  # dt <- test
  # nearshore_var <- "nearshore_slope_mean"
  # inlake_var <- "inlake_slope_pnt"
  rsq <- round(broom::glance(
    lm(as.formula(paste0(nearshore_var, " ~ ", inlake_var)), data = dt)
    )$r.squared, 2)
  res <-  ggplot(data = dt) + 
    geom_point(aes(.data[[nearshore_var]], .data[[inlake_var]]), size = 1) +
    geom_smooth(aes(.data[[nearshore_var]], .data[[inlake_var]]), 
                method = "lm", se = FALSE) +
    # geom_rect(xmin = 0.28, xmax = 0.42, ymin = 0, ymax = 0.05,
    # alpha = 1, fill = "white") +
    annotate("label", x = 0.4, y = 0.52, label = paste0("R^2 == ", rsq),
                                  parse = TRUE, size = text_size-0.7) +
    # annotate("label", x = 0.27, y = 0.01, 
    #          label = get_formula(
    #            lm(inlake_slope_pnt ~ nearshore_slope_mean, data = test)), 
    #          size = text_size-0.85, fill = "white", label.size = NA) +
    # geom_abline(slope = 1, intercept = 0) +
    xlab(stringr::str_replace_all(nearshore_var, c("nearshore_" = ""))) +
    ylab(pad_str(stringr::str_replace_all(inlake_var, c("inlake_" = "")), 
                 18)) +
    xlim(c(0, 0.6)) + ylim(0, 0.6) +
    labs(color = "") +
    theme_opts +
    theme(axis.title = element_text(family = "mono", size = 8))

@@

text_size <- 2.5
cowplot::plot_grid(
  cowplot::plot_grid(
  cowplot::plot_grid(gg_scatter_shape + 
                       labs(color = "") +
                       # theme(axis.title.x = element_blank()) +
                       annotate("text", x = 2250, y = 300, label = "R^2 == 0.80",
                                parse = TRUE, size = text_size) +
                       theme_opts,
                     gg_spacer,
                     gg_scatter_reservoir + 
                       labs(color = "") +
                       # annotate("text", x = 1800, y = 500, label = "R^2 == 0.80",
                       #          parse = TRUE) +
                       theme(#axis.title.x = element_blank(), 
                             axis.title.y = element_blank()) +
                       theme_opts, 
                     ncol = 3, rel_widths = c(1, 0, 1)),
  cowplot::plot_grid(ggplot() + geom_blank() + 
                       theme_opts + theme(axis.line = element_blank()), 
                     gg_slope_shape +
                       annotate("text", x = 0.36, y = 0.03, label = "R^2 == 0.17",
                                parse = TRUE, size = text_size) +
                       theme_opts,
                     gg_spacer,
                     gg_slope_reservoir + 
                         # annotate("text", x = 0.3, y = 0.03, label = "R^2 == 0.17",
                         #        parse = TRUE) +
                       theme(axis.title.y = element_blank()) +
                       theme_opts,
                     ncol = 4, rel_widths = c(0.11, 1, 0.11, 1)), 
                     rel_widths = c(0.7, 1), nrow = 2), 
 legend_panel, rel_heights = c(1, 0.12), ncol = 1
)
```

@@

theme_opts <- cowplot::theme_cowplot() +
  theme(legend.position = "bottom", 
        legend.title = element_blank(), 
        panel.spacing = unit(1, "lines")) 
cowplot::plot_grid(
  gg_area + theme_opts +
    guides(color = guide_legend(nrow = 2, byrow = TRUE)),
  gg_depth + theme_opts + 
    theme(axis.title.y = element_blank(), 
          axis.text.y = element_blank(), 
          axis.line.y = element_blank(),
          axis.ticks.y = element_blank()) +
    guides(color = guide_legend(nrow = 2, byrow = TRUE)),
  rel_widths = c(1, 0.87))

```

>>>>

gg_pntrng_deepest <- st_drop_geometry(dt) %>%
  dplyr::filter(!is.na(reservoir_class)) %>%
  group_by(reservoir_class) %>%
  summarize(dist_deepest = list(tibble::enframe(
    quantile(dist_deepest, probs = c(0.05, 0.5, 0.95), na.rm = TRUE)))) %>%
  unnest() %>%
  tidyr::spread(name, value) %>%
  ggplot() +
  geom_pointrange(aes(x = reservoir_class, y = `50%`,
    ymin = `5%`, ymax = `95%`)) +
  ylab("Deepest point distance (m)") + xlab("")

gg_pntrng_viscenter <- st_drop_geometry(dt) %>%
  dplyr::filter(!is.na(reservoir_class)) %>%
  group_by(reservoir_class) %>%
  summarize(dist_viscenter = list(tibble::enframe(
    quantile(dist_viscenter, probs = c(0.05, 0.5, 0.95), na.rm = TRUE)))) %>%
  unnest() %>%
  tidyr::spread(name, value) %>%
  ggplot() +
  geom_pointrange(aes(x = reservoir_class, y = `50%`,
    ymin = `5%`, ymax = `95%`)) +
  ylab("Distance to lake center (m)") + xlab("")

@@

get_pnt_map <- function(x) {
  # x <- 3
  # x <- which(dt$llid == 257862)
  lg_example <- LAGOSUSgis::query_gis(
    "LAGOS_US_All_Lakes_1ha", "lagoslakeid", dt$llid[x])
  crs_example <- st_crs(
    raster(list.files(paste0("../data/", tolower(dt$state[x]), "_bathy"),
      include.dirs = TRUE, full.names = TRUE)[1])
  )
  st_crs(dt$pnt_deepest)   <- crs_example
  st_crs(dt$pnt_viscenter) <- crs_example

@@

# get_pnt_map(which(dt$llid == 5636))
# get_pnt_map(which(dt$llid == 257862))
# cowplot::plot_grid(get_pnt_map(which(dt$llid == 3791)) +
#                      ggtitle(3791),
#                    get_pnt_map(which(dt$llid == 2772)) +
#                      ggtitle(2772),
#                    get_pnt_map(which(dt$llid == 2655)) +
#                      ggtitle(2655),
#                    get_pnt_map(which(dt$llid == 1822)) +
#                      ggtitle(1822)
#                    )
```

@@

gg_scatter_slope <- function(x, y, dt) {
  ggplot(data = dt) +
    geom_point(aes(UQ(rlang::sym(x)), UQ(rlang::sym(y))))
}

@@

rsq <- round(broom::glance(lm(dist_viscenter ~ dist_deepest, data = dt))$r.squared, 2)
gg_dist_base <- st_drop_geometry(dt) %>%
  dplyr::filter(!is.na(shape_class)) %>%
  dplyr::filter(dist_viscenter >= dist_deepest) %>%
  dplyr::filter(dist_deepest < 3200) %>%
  ggplot(aes(x = dist_deepest, y = dist_viscenter)) +
  geom_point(size = 1) +
  geom_smooth(method = "lm", se = FALSE) +
  annotate("text", x = 2550, y = 400, label = paste0("R^2 == ", rsq),
    parse = TRUE, size = text_size - 0.7) +
  annotate("label", x = 1800, y = 150,
    label = get_formula(
      lm(dist_viscenter ~ dist_deepest, data = st_drop_geometry(dt))),
    size = text_size - 0.85, fill = "white", label.size = NA) +
  labs(color = "") +
  xlab("Deepest point distance (m)") +
  ylab("Distance to \n lake center (m)") +
  xlim(0, 3000) +
  theme_opts

@@

rsq <- round(broom::glance(lm(nearshore_slope_mean ~ inlake_slope_pnt, data = test))$r.squared, 2)
gg_slope_base <- ggplot(data = test) +
  geom_point(aes(nearshore_slope_mean, inlake_slope_pnt), size = 1) +
  geom_smooth(aes(nearshore_slope_mean, inlake_slope_pnt), method = "lm", se = FALSE) +
  geom_rect(xmin = 0.28, xmax = 0.42, ymin = 0, ymax = 0.05,
    alpha = 1, fill = "white") +
  annotate("text", x = 0.34, y = 0.05, label = paste0("R^2 == ", rsq),
    parse = TRUE, size = text_size - 0.7) +
  annotate("label", x = 0.27, y = 0.01,
    label = get_formula(
      lm(inlake_slope_pnt ~ nearshore_slope_mean, data = test)),
    size = text_size - 0.85, fill = "white", label.size = NA) +
  # geom_abline(slope = 1, intercept = 0) +
  xlab("Nearshore slope (mean)") +
  ylab("In-lake slope") +
  labs(color = "") +
  theme_opts

cowplot::plot_grid(
  ggdraw() +
    draw_label("True measures", y = 0.37, hjust = 0, size = 12, angle = 90,  fontface = "bold"),
  cowplot::plot_grid(
    cowplot::plot_grid(
      gg_dist_base,
      gg_slope_base,
      rel_widths = c(1, 0.9)
    ),
    ggdraw() +
      draw_label("Proxy measures", x = 0.45, hjust = 0, size = 12, fontface = "bold"),
    ncol = 1, rel_heights = c(1, 0.1)),
  ncol = 2, rel_widths = c(0.1, 1))
```

@@

gg_dists_base <- dt %>%
  # dplyr::filter(!is.na(shape_class)) %>%
  dplyr::filter(dist_viscenter >= dist_deepest) %>%
  dplyr::filter(dist_deepest < 3200) %>%
  ggplot(aes(x = dists_deepest, y = dist_viscenter)) +
  geom_point(size = 1) +
  geom_smooth(method = "lm", se = FALSE) +
  annotate("text", x = 1800, y = 400, label = paste0("R^2 == ", rsq),
    parse = TRUE, size = text_size - 0.7) +
  annotate("label", x = 1200, y = 150,
    label = get_formula(
      lm(dist_viscenter ~ dists_deepest, data = dt)),
    size = text_size - 0.85, fill = "white", label.size = NA) +
  labs(color = "") +
  xlab("Deepest point distance (m)") +
  ylab("Distance to \n lake center (m)") +
  xlim(0, 2000) +
  theme_opts

@@

gg_slope_alternative <- function(nearshore_var, inlake_var, dt) {
  # dt <- test
  # nearshore_var <- "nearshore_slope_mean"
  # inlake_var <- "inlake_slope_pnt"
  rsq <- round(broom::glance(
    lm(as.formula(paste0(nearshore_var, " ~ ", inlake_var)), data = dt)
  )$r.squared, 2)
  res <-  ggplot(data = dt) +
    geom_point(aes(.data[[nearshore_var]], .data[[inlake_var]]), size = 1) +
    geom_smooth(aes(.data[[nearshore_var]], .data[[inlake_var]]),
      method = "lm", se = FALSE) +
    # geom_rect(xmin = 0.28, xmax = 0.42, ymin = 0, ymax = 0.05,
    # alpha = 1, fill = "white") +
    annotate("label", x = 0.4, y = 0.52, label = paste0("R^2 == ", rsq),
      parse = TRUE, size = text_size - 0.7) +
    # annotate("label", x = 0.27, y = 0.01,
    #          label = get_formula(
    #            lm(inlake_slope_pnt ~ nearshore_slope_mean, data = test)),
    #          size = text_size-0.85, fill = "white", label.size = NA) +
    # geom_abline(slope = 1, intercept = 0) +
    xlab(stringr::str_replace_all(nearshore_var, c("nearshore_" = ""))) +
    ylab(pad_str(stringr::str_replace_all(inlake_var, c("inlake_" = "")),
      18)) +
    xlim(c(0, 0.6)) + ylim(0, 0.6) +
    labs(color = "") +
    theme_opts +
    theme(axis.title = element_text(family = "mono", size = 8))

@@

text_size <- 2.5
cowplot::plot_grid(
  cowplot::plot_grid(
    cowplot::plot_grid(gg_scatter_shape +
      labs(color = "") +
      # theme(axis.title.x = element_blank()) +
      annotate("text", x = 2250, y = 300, label = "R^2 == 0.80",
        parse = TRUE, size = text_size) +
      theme_opts,
    gg_spacer,
    gg_scatter_reservoir +
      labs(color = "") +
      # annotate("text", x = 1800, y = 500, label = "R^2 == 0.80",
      #          parse = TRUE) +
      theme( # axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
      theme_opts,
    ncol = 3, rel_widths = c(1, 0, 1)),
    cowplot::plot_grid(ggplot() + geom_blank() +
      theme_opts + theme(axis.line = element_blank()),
    gg_slope_shape +
      annotate("text", x = 0.36, y = 0.03, label = "R^2 == 0.17",
        parse = TRUE, size = text_size) +
      theme_opts,
    gg_spacer,
    gg_slope_reservoir +
      # annotate("text", x = 0.3, y = 0.03, label = "R^2 == 0.17",
      #        parse = TRUE) +
      theme(axis.title.y = element_blank()) +
      theme_opts,
    ncol = 4, rel_widths = c(0.11, 1, 0.11, 1)),
    rel_widths = c(0.7, 1), nrow = 2),
  legend_panel, rel_heights = c(1, 0.12), ncol = 1
)
```

@@

theme_opts <- cowplot::theme_cowplot() +
  theme(legend.position = "bottom",
    legend.title = element_blank(),
    panel.spacing = unit(1, "lines"))
cowplot::plot_grid(
  gg_area + theme_opts +
    guides(color = guide_legend(nrow = 2, byrow = TRUE)),
  gg_depth + theme_opts +
    theme(axis.title.y = element_blank(),
      axis.text.y = element_blank(),
      axis.line.y = element_blank(),
      axis.ticks.y = element_blank()) +
    guides(color = guide_legend(nrow = 2, byrow = TRUE)),
  rel_widths = c(1, 0.87))
```
